### 2021-04-08 input/figaddA.tex
reworkd figures

  \draw[fill=white] (-\X, 0) node{$\bm{a}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
  \draw[fill=white] (0, 0) node{$\bm{b}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (\X, 0) node{$\bm{c}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (0, \Y) node{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  \draw (-\X, 5pt) node[above, color=\PA]{$\ADD_a^0$};
  \draw (\X, 5pt) node[above, color=\PC]{$\ADD_c^0$};

>>>>

  \draw[fill=white] (-\X, 0) node[color=\PA]{$\bm{a}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
  \draw[fill=white] (0, 0) node{$\bm{b}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (\X, 0) node{$\bm{c}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (0, \Y) node[color=\PD]{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  \draw (-\X, 5pt) node[above, font=\small, color=\PA]{$\ADD_a^0$};
  \draw (-5pt, \Y) node[left, font=\small, color=\PD]{$\ADD_d^0$};

### 2021-04-08 input/figdelA.tex
coloring figures, adding biblio, sketching abstract
reworkd figures

@@

  \newcommand\ADD{Add}
  \newcommand\DEL{Del}

  \draw (-\X, 0) -- node[above,font=\tiny]{$\ADD_{a, 1.5}$} (0, 0); %% a - b
  \draw (0, 0) -- node[above, font=\tiny]{$\ADD_{c, 1}$} (\X, 0); %% b - c
  \draw (0, 0) -- (0, \Y); %% b - d
  \draw (\X, 0) -- node[below, font=\tiny, sloped]{$\ADD_{c, 1}$} (0, \Y); %% c - d

  \draw[fill=white] (-\X, 0) node{$\bm{a}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
  \draw[fill=white] (0, 0) node{$\bm{b}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (\X, 0) node{$\bm{c}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (0, \Y) node{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  \draw (-\X+5pt, 5pt) node[above left]{$\DEL_a$};
  \draw (\X+5pt, 5pt) node[above right]{$\DEL_c$};

>>>>

  \thickmuskip=0mu
  \medmuskip=0mu
  \thinmuskip=0mu

@@

  \newcommand\ADD{\alpha}
  \newcommand\DEL{\delta}

  \draw (-\X + 5pt, 0) --
  node[above=-0.3em,font=\tiny]{$\DEL_{a} \rightarrow$}
  (0 - 5pt, 0); %% b - a

  \draw (0 +5pt, 0) --
  (\X -5pt, 0); %% b - c

  \draw (0, 0 - 5pt) --
  (0, \Y - 5pt);  %% d - b

  \draw (\X + 3pt, 0 - 5pt) --
  (0 + 5pt, \Y - 3pt); %% c - d

  \draw[fill=white] (-\X, 0) node{$\bm{a}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
  \draw[fill=white] (0, 0) node[color=\PD]{$\bm{b}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (\X, 0) node[color=\PD]{$\bm{c}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (0, \Y) node[color=\PD]{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  \draw (-\X, 5pt) node[above, font=\small]{$\DEL_a$};
  \draw (0, 5pt) node[above, font=\small, color=\PD]{$\ADD_d^1$};
  \draw (\X, 5pt) node[above, font=\small, color=\PD]{$\ADD_d^2$};
  \draw (-5pt, \Y) node[left, font=\small, color=\PD]{$\ADD_d^0$};
